No Title

### 2017-10-28 Paper/paper.tex
minor edits

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

@@

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

@@

This is a simple template for authors to write new MNRAS papers.
See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
for a full user guide.

\cite{Forero2009}.

\section{Illustris Simulation}
Illustris-1, also known as Illustris, is a highly resolved
cosmological simulation. It reproduces large-scale statistical
features of the Universe, such as the galaxy population of massive
clusters, as well as small-scale properties such as the morphology of
galaxies and detailed values for their stellar and gas content.\\

This was achieved by following the evolution of $2 \times 1820^3$ elements with dark mass resolution of $m_{\text{DM}} = 6.26\cdot 10^6\text{M}_{\odot}$ and initial baryonic mass resolution of $\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ from a glass-like configuration in a periodic box of $106.5\text{Mpc}$. The $\Lambda \text{CDM}$ cosmology of this run follows: $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
^{-1}\text{Mpc}^{-1}$ which is consistent with the (last) Anisotropy
Probe (WMAP)-9 \cite{AnisotropyProbe}. Illustris has a constant
spatial resolution of $1.4\text{kpc}$ for DM particles in comoving
units, and for baryonic particles it has the same spatial resolution
of DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$
in physical units for the rest of the simulation. \\

The evolution in time was performed with the hydrodynamic code AREPO
\cite{Arepo}, which combines a moving Voronoi tessellation with the
finite volume approach. Included in the evolution algorithm, there are
galaxy formation models which account for the evolution of stars and
SMBHs. Specifically, the physics followed by this model includes
energetic feedback from supermassive black holes and supernovae, as
well as stellar evolution and chemical enrichment. This level of
detail in Illustris is advantageous for the analysis of the effect of
the environment in barionic properties of galaxies. This level of resolution is hard to find
among other simulations, i.e. post-processed runs with semi-analytical
models which do not directly simulate baryons.(Expand) Describe Arepo more\\

@@

\subsection{ Characterizing Mass Functions}
A mass function is the number density $n(M)$ of objects of determined mass $M$.
Due to the large range of orders of magnitud in which these quantities span, the mass function is often represented in logarithmic scales on both sides. 
The discretization of these mass functions is simply the histogram of the logarithmic masses of the studied group of objects. 
In Illustris, as in all simulations, we have clear determination of volumes. This volume is constant over all the sample of galaxies studied and is to be taken the constant volume of the simulation $V = \left(106.5\text{Mpc}\right)^3$. 
In this sense, the relation expressed by a mass function is

\begin{equation}
n(M)Vd\log{(M)} =  dN
\end{equation}

To characterize specific properties of these mass functions, we use the Press-Schechter function \ref{eq:Schechter}. 
It comes from an elaborated formalism of hierarchical formation of DM structures in an expanding Friedmann universe arriving to a self-similar state of "equilibrium" for its mass function \cite{Schechter1976}.
Although its ansatz has been demonstrated to be inaccurate for our observable universe \cite{inaccurateSchechter}, the final expression is very well fitted to the mass functions of the local universe \cite{wellfitSchechter}.\\

\begin{equation}
n\left( M \right) = n_*\left( \frac{M}{M_*} \right)^{-\alpha+1}\exp^{-\left( \frac{M}{M_*}\right)}
\label{eq:Schechter}
\end{equation}

The Schechter function \ref{eq:Schechter} is fully defined by the three parameters $(n_*,M_*,\alpha)$. 
The number density factor $n_*$ is just a normalization factor which varies depending on the studied system. 
The mass scale factor $M_*$ may be interpreted as the mass that separates the power-law regimen $M \ll M_*$ and the exponential regimen $M \gg M_*$. 
This transition graphically resemnles a knee, which is the reason why $M_*$ is referred as the knee-mass.
The faint-end slope $\alpha$ is directly related to the exponent of the power-law at the low-mass regime.
In logarithmic scales, it is clearly interpreted as the slope of the low-mass regime.\\

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

@@

% Abstract of the paper
\begin{abstract}
No abstract.
\end{abstract}

@@

\section{The Illustris-1 Simulation}
Illustris-1 is a highly resolved cosmological simulation. 
It reproduces large-scale statistical features of the Universe, such
as the galaxy population of massive clusters, as well as small-scale
properties such as the morphology of galaxies and detailed values for
their stellar and gas content.

The Illustris-1 simulation followed  the evolution of $2 \times 1820^3$
elements with dark mass resolution of $m_{\text{DM}} = 6.26\cdot
10^6\text{M}_{\odot}$ and initial baryonic mass resolution of
$\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ from a
glass-like configuration in a periodic box of $106.5\text{Mpc}$. The
$\Lambda \text{CDM}$ cosmology of this run follows:
$\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$,
$\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0809$,
$\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms} 
^{-1}\text{Mpc}^{-1}$ which is consistent with the (last) Anisotropy
Probe (WMAP)-9 \cite{AnisotropyProbe}. Illustris has a constant
spatial resolution of $1.4\text{kpc}$ for DM particles in comoving
units, and for baryonic particles it has the same spatial resolution
of DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$
in physical units for the rest of the simulation. \\

This work was  performed using the hydrodynamic code AREPO
\cite{Arepo}, which combines a moving Voronoi tessellation with the
finite volume approach. Included in the evolution algorithm, there are
galaxy formation models which account for the evolution of stars and
SMBHs. Specifically, the physics followed by this model includes
energetic feedback from supermassive black holes and supernovae, as
well as stellar evolution and chemical enrichment. This level of
detail in Illustris is advantageous for the analysis of the effect of
the environment in barionic properties of galaxies. This level of resolution is hard to find
among other simulations, i.e. post-processed runs with semi-analytical
models which do not directly simulate baryons.(Expand) Describe Arepo more\\

@@

\subsection{ Characterizing Mass Functions}

To characterize specific properties of these mass functions, we use
the Press-Schechter function
\begin{equation}
n(M) = n_\star\left( \frac{M}{M_\star} \right)^{-\alpha+1}\exp^{-\left( \frac{M}{M_\star}\right)},
\label{eq:Schechter}
\end{equation}
%
where $n$ is the number of galaxies per unit volume per dex in mass.
This function is fully described by the three parameters: $n_\star$,
$M_\star$ and $\alpha$; $n_\star$ is a normalization factor, the mass
scale factor $M_\star$ is that separates the power-law regimen at $M
\ll M_*$ and the exponential regimen for $M \gg M_*$. 
This transition graphically resembles a knee, which is the reason why
we refer in this paper $M_*$ as the knee-mass.
The faint-end slope $\alpha$ is directly related to the exponent of the power-law at the low-mass regime.
In logarithmic scales, it is clearly interpreted as the slope of the low-mass regime.\\

and the scalars $n_{\star}$, $M_{\star}$ and $\alpha$ are 
$M$.

It comes from an elaborated formalism of hierarchical formation of DM structures in an expanding Friedmann universe arriving to a self-similar state of "equilibrium" for its mass function \cite{Schechter1976}.
Although its ansatz has been demonstrated to be inaccurate for our
observable universe \cite{inaccurateSchechter}, the final expression
is very well fitted to the mass functions of the local universe
\cite{wellfitSchechter}.\\
